An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-19 draft.tex
Revised and fixed some things

This reactive architecture has the following advantages:\begin{itemize}
\item 
An important aspect of proposal is the decoupling of the population and 
the population-based algorithm. It is common that in a classic island-based algorithm
each island is executed in a separate processing node, i.e. in a virtual machine, cpu,
or thread. In this case we can have just one processing node, or many nodes, each 
running a different search strategy, or using its own parameters. 
\item 
Also, the reactive controller, gives designers more control over the milti-population algorithm.
In this process, designers can dynamicly change the number of populations, population parameters,
and migration details on-the-fly.
\item 
Another advantege is that algorithm designers have many options for implementing this simple architecure. 
The same basic components can be implmented as a single multithreaded program, or 
as a highly scalable serverless cloud application. Most modern languages include 
constructs for asynchronous programming using queues or channels, for a multi-threaded
execution.
\end{itemize}

@@

\subsection{Comparasion} 
\label{edm}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{population_message}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
    \label{fig:kafkEO}
\end{figure}

>>>>

This reactive architecture has the following advantages:\begin{itemize}
\item 
An important aspect of proposal is the decoupling of the population and 
the population-based algorithm. It is common that in a classic island-based algorithm
each island is executed in a separate processing node, i.e. in a virtual machine, cpu,
or thread. In this case we can have just one processing node, or many nodes, each 
running a different search strategy, or using its own parameters. 
\item 
Also, the reactive controller gives designers more control over the multi-population algorithm.
In this process, designers can dynamicly change the number of populations, population parameters,
and migration details on-the-fly.
\item 
Another advantege is that algorithm designers have many options for implementing this simple architecture. 
The same basic components can be implmented as a single multithreaded program, or 
as a highly scalable serverless cloud application. Most modern languages include 
constructs for asynchronous programming using queues or channels, for a multi-threaded
execution.
\end{itemize}

@@

\subsection{Comparison} 
\label{edm}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{population_message}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)} % Er, same caption. Better insert it now, or we might roftet... Also, same label. - JJ
    \label{fig:kafkEO}
\end{figure}
